Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements

### 2025-01-04 Submission.tex
tried applying vancouver style

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

Two related theories serve as the foundation for the current study: the job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) and Cavanaugh et al. (2000)'s challenge-hindrance stressor framework. The job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

Cavanaugh et al. (2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors/demands (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility (M. A. LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity (M. A. LePine, 2022).

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000). Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J. A. LePine et al. (2005) regarding performance and Crawford et al. (2010) regarding engagement).

M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Demands appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022).

Recent work affirms these appraisal processes. Pindek et al. (2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M. A. LePine (2022) above). As expected, hindrance demands had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Pindek et al. (2024) notes this limitation of \emph{a priori} classification of characteristics as demands, challenges, or hindrances, as do Horan et al. (2020). In fact, although much of our research on job demands based on \emph{a priori} classifications (Searle \& Auton, 2015), the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

Aligned with this dynamic perspective on the experience of work, Horan et al. (2020) and M. A. LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).

Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011). For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge. Webster et al. (2011) approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000). Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J. A. LePine et al., 2005). We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \ref{fig:ourmodel} for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, Hakanen et al. (2008) found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).

@@

The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example. Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).

Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress. When a demand is appraised as a hindrance -- it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000). Chen et al. (2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007). Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas \& Raja, 2019; J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions (see Figure \ref{fig:ourmodel}):

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007). Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. Bakker et al. (2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, Xanthopoulou et al. (2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \ref{fig:ourmodel}):

@@

Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample. Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Respondent ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).

@@

The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001). The O*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated. We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

@@

Similarly, hindrance demands and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj. \(R^2\) = 0.03, \(F(2, 565) = 10.68\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect {[}see Figure \ref{fig:hind-resource-burn-int}{]}. As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources. Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.

@@

The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes. We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand (particularly challenge demands). The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands. This finding lends additional evidence to Horan et al. (2020)'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). While we did not find support for the prediction that different types of demands would be related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).

@@

The findings presented above have implications for both theory and practice. First, this research is situated within the familiar job demands-resources theory (Demerouti et al., 2001). Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics. In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011). This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000). Further, Cavanaugh et al. (2000) suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000), which we partially supported here.

Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon more so that what is seen a hindrance. In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire. For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort. Such conversations could happen during an annual performance review. In addition, J. A. LePine et al. (2005) and Podsakoff et al. (2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged. The current results suggest that these activities and training sessions would ideally be personalized.

@@

We also retained the literature-derived definitions of resources, challenges, and hindrances (Demerouti et al., 2001). Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended. Future investigations may wish to explore the colloquial versus academic phrasing of these questions and how that may impact observed associations between resources and challenges. We also note that effect sizes were small and thus it is important to consider the practical significance when thinking about potential interventions. We encourage future thought on how consideration of resource and demand perceptions might be combined with moderators to reduce employee stress and burnout, as well as enhance engagement.

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-abbas2019challenge}
Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.

\bibitem[\citeproctext]{ref-bakker2014job}
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\bibitem[\citeproctext]{ref-bakker2017job}
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\bibitem[\citeproctext]{ref-bakker2005job}
Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.

\bibitem[\citeproctext]{ref-bakker2007job}
Bakker, A. B., Hakanen, J. J., Demerouti, E., \& Xanthopoulou, D. (2007). Job resources boost work engagement, particularly when job demands are high. \emph{Journal of Educational Psychology}, \emph{99}(2), 274.

\bibitem[\citeproctext]{ref-bakker2013weekly}
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\bibitem[\citeproctext]{ref-chen2021daily}
Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.

\bibitem[\citeproctext]{ref-crawford2010linking}
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\bibitem[\citeproctext]{ref-demerouti2001job}
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\bibitem[\citeproctext]{ref-gerich2017relevance}
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

\bibitem[\citeproctext]{ref-hakanen2008job}
Hakanen, J. J., Schaufeli, W. B., \& Ahola, K. (2008). The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement. \emph{Work \& Stress}, \emph{22}(3), 224--241.

>>>>

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands {[}1{]} or that appraisals may change over time {[}2{]}. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

Two related theories serve as the foundation for the current study: the job demands-resources theory {[}e.g., 3,4{]} and {[}5{]}'s challenge-hindrance stressor framework. The job demands-resources theory {[}e.g., 3,4{]} highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development {[}e.g., 3,4{]}. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}high work pressure, for example, is commonly cited as a demand, e.g., 6{]}. The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; {[}3{]}).

{[}5{]} proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from {[}7{]}'s perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors/demands {[}e.g., 5{]}. Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility {[}8{]}. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity {[}8{]}.

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes {[}e.g., 5{]}. Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, {[}9{]} regarding performance and {[}10{]} regarding engagement).

{[}8{]} explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Demands appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions {[}8{]}.

Recent work affirms these appraisal processes. {[}11{]} meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by {[}8{]} above). As expected, hindrance demands had both direct and indirect (through strain) associations with performance {[}11{]}.

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. {[}11{]} notes this limitation of \emph{a priori} classification of characteristics as demands, challenges, or hindrances, as do {[}12{]}. In fact, although much of our research on job demands based on \emph{a priori} classifications {[}13{]}, the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

Aligned with this dynamic perspective on the experience of work, {[}12{]} and {[}8{]} specifically call out the need for additional research to incorporate the appraisal process described by {[}7{]} into the challenge-hindrance stressor framework. In fact, {[}12{]} state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time {[}e.g., 13{]}.

Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands {[}1,e.g., 14,15{]}. For example, {[}14{]} found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge. {[}1{]} approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- {[}4{]} and challenge-hindrance stressor-frameworks {[}5{]}. Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance {[}e.g., 9{]}. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \ref{fig:ourmodel} for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development {[}e.g., 3,4{]}, and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, {[}16{]} found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, {[}17{]} found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement {[}e.g., 18{]}.

@@

The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work {[}19{]}, engagement {[}10{]}, and strain and turnover intentions {[}e.g., 20{]}, for example. Challenge appraisals have been negatively associated with job search behaviors {[}e.g., 5{]}.

Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress. When a demand is appraised as a hindrance -- it is negatively associated with motivational resources {[}21{]}, engagement {[}10{]}, job search behaviors and job satisfaction {[}5{]}. {[}19{]} found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands {[}22{]}. Interestingly, both challenges and hindrances have been shown to positively predict strain {[}9,20,22,23{]}, which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions (see Figure \ref{fig:ourmodel}):

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain {[}e.g., 24{]} and burnout {[}e.g., 25{]}. Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. {[}24{]} explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, {[}25{]} also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \ref{fig:ourmodel}):

@@

Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses {[}26{]}. Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample. Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Respondent ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).

@@

The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations {[}27{]}. The O*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated. We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

@@

Similarly, hindrance demands and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj. \(R^2\) = 0.03, \(F(2, 565) = 10.68\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect (see Figure \ref{fig:hind-resource-burn-int}). As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources. Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.

@@

The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes. We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand (particularly challenge demands). The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands. This finding lends additional evidence to {[}12{]}'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). While we did not find support for the prediction that different types of demands would be related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).

@@

The findings presented above have implications for both theory and practice. First, this research is situated within the familiar job demands-resources theory {[}6{]}. Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics. In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs {[}1{]}. This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely {[}7{]}, and thus, could appraise them as either a challenge or hindrance to their job performance {[}5{]}. Further, {[}5{]} suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes {[}e.g., 5{]}, which we partially supported here.

Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon more so that what is seen a hindrance. In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire. For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort. Such conversations could happen during an annual performance review. In addition, {[}9{]} and {[}22{]} encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged. The current results suggest that these activities and training sessions would ideally be personalized.

@@

We also retained the literature-derived definitions of resources, challenges, and hindrances {[}6{]}. Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended. Future investigations may wish to explore the colloquial versus academic phrasing of these questions and how that may impact observed associations between resources and challenges. We also note that effect sizes were small and thus it is important to consider the practical significance when thinking about potential interventions. We encourage future thought on how consideration of resource and demand perceptions might be combined with moderators to reduce employee stress and burnout, as well as enhance engagement.

@@

\phantomsection\label{refs}
\begin{CSLReferences}{0}{0}
\bibitem[\citeproctext]{ref-webster2011extending}
\CSLLeftMargin{{[}1{]} }%
\CSLRightInline{Webster JR, Beehr TA, Love K. Extending the challenge-hindrance model of occupational stress: The role of appraisal. Journal of Vocational Behavior 2011;79:505--16.}

\bibitem[\citeproctext]{ref-rosen2020challenges}
\CSLLeftMargin{{[}2{]} }%
\CSLRightInline{Rosen CC, Dimotakis N, Cole MS, Taylor SG, Simon LS, Smith TA, et al. When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes. Journal of Applied Psychology 2020;105:1181.}

\bibitem[\citeproctext]{ref-bakker2014job}
\CSLLeftMargin{{[}3{]} }%
\CSLRightInline{Bakker AB, Demerouti E. Job demands--resources theory. Wellbeing: A Complete Reference Guide 2014:1--28.}

\bibitem[\citeproctext]{ref-bakker2017job}
\CSLLeftMargin{{[}4{]} }%
\CSLRightInline{Bakker AB, Demerouti E. Job demands--resources theory: Taking stock and looking forward. Journal of Occupational Health Psychology 2017;22:273.}

\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
\CSLLeftMargin{{[}5{]} }%
\CSLRightInline{Cavanaugh MA, Boswell WR, Roehling MV, Boudreau JW. An empirical examination of self-reported work stress among US managers. Journal of Applied Psychology 2000;85:65.}

\bibitem[\citeproctext]{ref-demerouti2001job}
\CSLLeftMargin{{[}6{]} }%
\CSLRightInline{Demerouti E, Bakker AB, Nachreiner F, Schaufeli WB. The job demands-resources model of burnout. Journal of Applied Psychology 2001;86:499.}

\bibitem[\citeproctext]{ref-lazarus1984stress}
\CSLLeftMargin{{[}7{]} }%
\CSLRightInline{Lazarus RS, Folkman S. Stress, appraisal, and coping. Springer publishing company; 1984.}

\bibitem[\citeproctext]{ref-lepine2022challenge}
\CSLLeftMargin{{[}8{]} }%
\CSLRightInline{LePine MA. The challenge-hindrance stressor framework: An integrative conceptual review and path forward. Group \& Organization Management 2022;47:223--54.}

\bibitem[\citeproctext]{ref-lepine2005meta}
\CSLLeftMargin{{[}9{]} }%
\CSLRightInline{LePine JA, Podsakoff NP, LePine MA. A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance. Academy of Management Journal 2005;48:764--75.}

\bibitem[\citeproctext]{ref-crawford2010linking}
\CSLLeftMargin{{[}10{]} }%
\CSLRightInline{Crawford ER, LePine JA, Rich BL. Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. Journal of Applied Psychology 2010;95:834.}

\bibitem[\citeproctext]{ref-pindek2024dynamic}
\CSLLeftMargin{{[}11{]} }%
\CSLRightInline{Pindek S, Meyer K, Valvo A, Arvan M. A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies. Journal of Business and Psychology 2024:1--19.}
